---
title: "Lab 3 Linear Regression"
output: html_notebook
---
#Linear Regression Lab

```{r}
#load library
library(MASS)
library(ISLR)
```

```{r}
fix(Boston)
names(Boston)
```
##Linear model with lm()
```{r}
#lm.fit=lm(medv~lstat,data=Boston)
attach(Boston)
lm.fit=lm(medv~lstat)
lm.fit
```

##Get summary
```{r}
summary(lm.fit)
```

##Coefficients
```{r}
coef(lm.fit) #lm.fit$coefficients
```

##Confidence Interval
```{r}
confint(lm.fit)
```

##Predict for medv
```{r}
predict(lm.fit,data.frame(lstat=c(5,10,15)),interval="confidence")
```

##Plot
```{r}
plot(lstat,medv)
abline(lm.fit)
```

##Further plots
I will not test further plot() cause in industry we always use packages like 'ggplot2'

#Multiple Linear Regression
```{r}
lm.fit=lm(medv~lstat+age,data=Boston)
summary(lm.fit)
```

##With all vars
```{r}
lm.fit=lm(medv~.,data=Boston)
summary(lm.fit)
```

##Variance Inflation Factor
```{r}
library(car)
vif(lm.fit)
```

##Elim age since p is too high
```{r}
lm.fit1=lm(medv~.-age,data=Boston)
summary(lm.fit1)
```

##Interaction terms
```{r}
summary(lm(medv~lstat*age,data=Boston))
```

##Non-Linear transformation
```{r}
lm.fit2=lm(medv~lstat+I(lstat^2))
summary(lm.fit2)
```

##Compare the importance of quadratic term
```{r}
lm.fit=lm(medv~lstat)
anova(lm.fit, lm.fit2)
```

##Plot
```{r}
par(mfrow=c(2,2))
plot(lm.fit2)
```

##^5 fit
```{r}
lm.fit5=lm(medv~poly(lstat,5))
summary(lm.fit5)
```

##Log transformation
```{r}
summary(lm(medv~log(rm),data=Boston))
```

#Qualitive Predictors
```{r}
fix(Carseats)
names(Carseats)
attach(Carseats)
```

##Go with it
```{r}
lm.fit=lm(Sales~.+Income:Advertising+Price:Age,data=Carseats)
summary(lm.fit)
```